---
title: "Here are some plotly plots"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

Interactivity is great. 

We often make plots in DS.

Here's the tidyverse.
```{r message=FALSE}
library(tidyverse)
library(plotly)

library(p8105.datasets)
```


Let's load the airbnb dataset.

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```


Let's make a scatterplot. but interactive this time.

```{r}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |> 
  plot_ly(
    x = ~lat, y = ~long, 
    type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

Let's make a boxplot.

`neighbourhood = fct_reorder(neighbourhood, price)` organize/order by price!

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

Let's make a barchart!

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```



## gpplots

* I use ggplot for static plots, and I make static plots way, way more frequently than interactive plots. Sometimes I’ll use ggplotly on top of that for some quick interactivity; this can be handy to do some zooming or inspect outlying features.
* just for you, not to share.

```{r}
scatter_ggplot = 
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

